Paper_analysisandtables

### 2024-12-20 Code/Paper_analysisandtables.Rmd
Final figure updates

Compositestable <- capture.output(stargazer(compositemodellist,
                                 type = 'html', 
                                 column.labels = c("coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Water quality", "Affordability", 
                                                    "TMF"), 
                                 ci=c(F,T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 p = c(p.valuesWQ1, p.values2, pvaluesAffordability1, p.values2,
                                       pvaluesTMF1, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Lim enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased"),
                                 omit = "Constant",
                                apply.ci = function(x) { 0 }))

@@

WQtable <- capture.output(stargazer(WQmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("ecoli", "treatment technique violations", "MCL violations", 
                                                    "cont. of emerging concern"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 p = c(pvaluesecoli, p.values2, pvaluesTT, p.values2,
                                       pvaluesMCL, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Lim enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

AFtable <- capture.output(stargazer(AFmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("bill ≥1.5% MHI", "bill ≥150% statewide average",
                                                    "did not apply for arrearage relief", "no funding"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 p = c(pvaluesMHI, p.values2, pvaluesextreme, p.values2, pvaluescovid, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Lim enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

TMFtable <- capture.output(stargazer(TMFmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio", 
                                                   "coefficients(se)", "Odds ratio"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("operator cert violations", "M&R violations", "Cash on hand"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 p = c(pvaluesOpcert, p.values2, pvaluesmrviolations, p.values2, pvaluescash, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Lim enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

```{r descriptives for demofraphics, results='asis', echo=FALSE}
Data_mini <- Data %>% select(enfranchisement_final, MHI_KD, MHI, LN_POP, Source, Percent.renter, Percent.white, POPULATION, CALENVIRO_SCREEN_SCORE, FAILING, WQ_combined_any, Affordability_combined_any, TMF_combined_any, Accessibility_combined_any, Percent.hispanicorlatino, Percent.black, Percent.asian)

Descriptives<- Data_mini %>%
  group_by(enfranchisement_final) %>% 
  summarize(meanPOP = mean(na.omit(POPULATION)),
            meanMHI_KD = mean(na.omit(MHI_KD)),
            meanMHI = mean(na.omit(MHI)),
            meanPercRent = mean(na.omit(Percent.renter)),
            meanPercWhite = mean(na.omit(Percent.white)),
            meanCES = mean(na.omit(CALENVIRO_SCREEN_SCORE)),
            medianpop = median(na.omit(POPULATION)))

@@

```{r dem sig tests, results='asis', echo=FALSE}
#ANOVA and Tukey HSD
MHI <- aov(MHI_KD ~ enfranchisement_final, data = Data)
summary(MHI)
TukeyMHI <- TukeyHSD(MHI)
TukeyMHI_table <- as.data.frame(TukeyMHI$enfranchisement_final)

AA <- aov(Percent.black ~ enfranchisement_final, data = Data)
summary(AA)
TukeyAA <- TukeyHSD(AA)
TukeyAA_table <- as.data.frame(TukeyAA$enfranchisement_final)
```

>>>>

Compositestable <- capture.output(stargazer(compositemodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Water quality", "Affordability", 
                                                    "TMF capacity"), 
                                 ci=c(F,T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(p.valuesWQ1, p.values2, pvaluesAffordability1, p.values2,
                                       pvaluesTMF1, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Limited enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                apply.ci = function(x) { 0 }))

@@

WQtable <- capture.output(stargazer(WQmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("E. coli", "Treatment technique violations", "MCL violations"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesecoli, p.values2, pvaluesTT, p.values2,
                                       pvaluesMCL, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Limited enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

AFtable <- capture.output(stargazer(AFmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Unaffordable bill", "Extreme bill",
                                                    "No arrearage relief"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesMHI, p.values2, pvaluesextreme, p.values2, pvaluescovid, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Limited enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

TMFtable <- capture.output(stargazer(TMFmodellist,
                                 type = 'html', 
                                 column.labels = c("coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR", 
                                                   "coefficient (se)", "OR"),
                                 model.numbers = FALSE, 
                                 dep.var.labels = c("Operator cert. violations", "M&R violations", "Cash on hand"), 
                                 ci=c(F,T, F, T, F, T, F, T), 
                                 star.cutoffs = c(0.05, 0.01, 0.001),
                                 notes="<span>&#42;&#42;&#42;</span>: p<0.001; <span>&#42;&#42;</span>: p<0.01;<span>&#42;</span>: p<0.05",
                                 notes.append = FALSE,
                                 p = c(pvaluesOpcert, p.values2, pvaluesmrviolations, p.values2, pvaluescash, p.values2),
                                 omit.stat = c("ll", "aic"),
                                 covariate.labels = c("Limited enfran.", "No enfran.",
                                                      "Population (log)", "Surface water",
                                                      "Purchased", "MHI", "Percent renter", "Percent non-Hispanic white"),
                                 omit = "Constant",
                                 apply.ci = function(x) { 0 }))

@@

```{r descriptives for demofraphics, results='asis', echo=FALSE}
Data_mini <- Data %>% select(enfranchisement_final, MHI, LN_POP, Source, Percent.renter, Percent.white, POPULATION, CALENVIRO_SCREEN_SCORE, FAILING, WQ_combined_any, Affordability_combined_any, TMF_combined_any, Accessibility_combined_any, Percent.hispanicorlatino, Percent.black, Percent.asian)

Descriptives<- Data_mini %>%
  group_by(enfranchisement_final) %>% 
  summarize(meanPOP = mean(na.omit(POPULATION)),
            meanMHI = mean(na.omit(MHI)),
            meanPercRent = mean(na.omit(Percent.renter)),
            meanPercWhite = mean(na.omit(Percent.white)),
            meanCES = mean(na.omit(CALENVIRO_SCREEN_SCORE)),
            medianpop = median(na.omit(POPULATION)))

@@

```{r dem sig tests, results='asis', echo=FALSE}
#ANOVA and Tukey HSD
MHI <- aov(MHI ~ enfranchisement_final, data = Data)
summary(MHI)
TukeyMHI <- TukeyHSD(MHI)
TukeyMHI_table <- as.data.frame(TukeyMHI$enfranchisement_final)

Data$Source_bi <- NA
Data$Source_bi <- ifelse(Data$Source == "GW", 1, Data$Source_bi)
Data$Source_bi <- ifelse(Data$Source == "SW", 0, Data$Source_bi)

GW <- aov(Data$Source_bi ~ Data$enfranchisement_final)
summary(GW)
TukeyGW <- TukeyHSD(GW)
TukeyGW_table <- as.data.frame(TukeyGW$`Data$enfranchisement_final`)

Pop <- aov(Data$POPULATION ~ Data$enfranchisement_final)
summary(Pop)
TukeyPop <- TukeyHSD(Pop)
TukeyPop_table <- as.data.frame(TukeyPop$`Data$enfranchisement_final`)

Rent <- aov(Data$Percent.renter ~ Data$enfranchisement_final)
summary(Rent)
TukeyRent <- TukeyHSD(Rent)
TukeyRent_table <- as.data.frame(TukeyRent$`Data$enfranchisement_final`)

CalE <- aov(Data$CALENVIRO_SCREEN_SCORE ~ Data$enfranchisement_final)
summary(CalE)
TukeyCalE <- TukeyHSD(CalE)
TukeyCalE_table <- as.data.frame(TukeyCalE$`Data$enfranchisement_final`)

White <- aov(Data$Percent.white ~ Data$enfranchisement_final)
summary(White)
TukeyWhite <- TukeyHSD(White)
TukeyWhite_table <- as.data.frame(TukeyWhite$`Data$enfranchisement_final`)

AA <- aov(Percent.black ~ enfranchisement_final, data = Data)
summary(AA)
TukeyAA <- TukeyHSD(AA)
TukeyAA_table <- as.data.frame(TukeyAA$enfranchisement_final)

Lat <- aov(Data$Percent.hispanicorlatino ~ Data$enfranchisement_final)
summary(Lat)
TukeyLat <- TukeyHSD(Lat)
TukeyLat_table <- as.data.frame(TukeyLat$`Data$enfranchisement_final`)

As <- aov(Data$Percent.asian ~ Data$enfranchisement_final)
summary(As)
TukeyAs <- TukeyHSD(As)
TukeyAs_table <- as.data.frame(TukeyAs$`Data$enfranchisement_final`)
